Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-20 paper-2023-acsos-pulverization.tex
finish up section 4

\usepackage{cleveref}
\usepackage{color}
\usepackage{nicefrac}

@@

\makeatletter
\newcommand{\linebreakand}{%
  \end{@IEEEauthorhalign}
  \hfill\mbox{}\par
  \mbox{}\hfill\begin{@IEEEauthorhalign}
}
\makeatother

@@

\subsubsection{Implementation}
We implemented our simulations by interfacing \ourframework{}
with the Alchemist Simulator~\cite{PianiniJOS2013}
through a dedicated platfrom module.
%
We ran experiments varying the number of participants (hence, smartphones): 100, 300, and 1000.
%
For each experiment, we run a total of 10 repetitions with a different random seed;
all results are averaged over them.
%
The experiment has been open sourced\footnote{\url{https://github.com/nicolasfara/ACSOS-2023-pulverization-evaluation}}
and the code has been archived on Zenodo~\cite{https://doi.org/10.5281/zenodo.7948801}.
%
\begin{figure}
    \includegraphics[width=\linewidth]{figures/simulation-screenshot.png}
    \caption{
        A snapshot of the large-scale simulation.
        Smartphones are represented as coloured circles,
        with the color indicating their battery level
        (green when charged, red when low).
    }
    \label{fig:simulation-screenshot}
\end{figure}
%
\Cref{fig:simulation-screenshot} shows a snapshot of the simulation

\subsubsection{Results}

\begin{figure}[ht]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\linewidth]{figures/cloud_cost-device_consumption-cloud_consumption-distance-device=100.0.pdf}
    \end{minipage}
    \caption{
        Results of the simulation with 100 devices.
        %
        The \emph{green} bar represents the mean power consumed by cloud;
        the \emph{blue} bar represents the mean power consumed by all the devices in the system;
        the \emph{yellow} bar represents the mean traveled distance by the people
        and the \emph{purple} bar represents the average cost per hour of the cloud.
        %
        The chart shows two ``static'' scenarios: \emph{device-only} (on the left) and \emph{cloud-only} (on the right).
        %
        All the intermediate scenarios are obtained by exploiting the reconfiguration capabilities of the pulverization framework,
        where different battery threshold are used to trigger the reconfiguration.
    }
    \label{fig:result-100-devices}
\end{figure}

\begin{figure}[ht]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\linewidth]{figures/cloud_cost-device_consumption-cloud_consumption-distance-device=300.0.pdf}
    \end{minipage}
    \caption{
        Results of the simulation with 300 devices.
        %
        The \emph{green} bar represents the mean power consumed by cloud;
        the \emph{blue} bar represents the mean power consumed by all the devices in the system;
        the \emph{yellow} bar represents the mean traveled distance by the people
        and the \emph{purple} bar represents the average cost per hour of the cloud.
        %
        The chart shows two ``static'' scenarios: \emph{device-only} (on the left) and \emph{cloud-only} (on the right).
        %
        All the intermediate scenarios are obtained by exploiting the reconfiguration capabilities of the pulverization framework,
        where different battery threshold are used to trigger the reconfiguration.
    }
    \label{fig:result-300-devices}
\end{figure}

\begin{figure}[ht]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\linewidth]{figures/cloud_cost-device_consumption-cloud_consumption-distance-device=1000.0.pdf}
    \end{minipage}
    \caption{
        Results of the simulation with 1000 devices.
        %
        The \emph{green} bar represents the mean power consumed by cloud;
        the \emph{blue} bar represents the mean power consumed by all the devices in the system;
        the \emph{yellow} bar represents the mean traveled distance by the people
        and the \emph{purple} bar represents the average cost per hour of the cloud.
        %
        The chart shows two ``static'' scenarios: \emph{device-only} (on the left) and \emph{cloud-only} (on the right).
        %
        All the intermediate scenarios are obtained by exploiting the reconfiguration capabilities of the pulverization framework,
        where different battery threshold are used to trigger the reconfiguration.
    }
    \label{fig:result-1000-devices}
\end{figure}

>>>>

\usepackage{cleveref}
\usepackage{color}
\usepackage{nicefrac}
\usepackage{wasysym}

@@

\makeatletter
\newcommand{\linebreakand}{
  \end{@IEEEauthorhalign}
  \hfill\mbox{}\par
  \mbox{}\hfill\begin{@IEEEauthorhalign}
}
\makeatother

@@

\subsubsection{Implementation}
We implemented our simulations by interfacing \ourframework{}
with the Alchemist Simulator~\cite{PianiniJOS2013}
through a dedicated platform module.
%
We ran experiments varying the number of participants (hence, smartphones): 100, 300, and 1000
and the \ourframework{} reconfiguration rules:
$\Uparrow$ (behaviour always in the smartphones),
$\Updownarrow^{60}_{20}$,
$\Updownarrow^{80}_{20}$,
$\Updownarrow^{60}_{40}$,
$\Updownarrow^{80}_{40}$,
$\Downarrow$ (behaviour always in the cloud).
%
All the hybrid configurations
(all except $\Uparrow$ and $\Downarrow$)
require runtime reconfiguration to be realised.
%
For each experiment, we run a total of 10 repetitions with a different random seed;
all results are averaged over them.
%
The experiment has been open sourced\footnote{\url{https://github.com/nicolasfara/ACSOS-2023-pulverization-evaluation}}
and the code has been archived on Zenodo~\cite{https://doi.org/10.5281/zenodo.7948801}.
%
\begin{figure}
    \includegraphics[width=\linewidth]{figures/simulation-screenshot.png}
    \caption{
        A snapshot of the large-scale simulation.
        Smartphones are represented as coloured circles,
        with the color indicating their battery level
        (green when charged, red when low).
    }
    \label{fig:simulation-screenshot}
\end{figure}
%
\Cref{fig:simulation-screenshot} shows a snapshot of the simulation

\subsubsection{Results}
%
\begin{figure*}
    \includegraphics[width=.32\linewidth]{figures/cloud_cost-device_consumption-cloud_consumption-distance-device=100.0.pdf}~
    \includegraphics[width=.32\linewidth]{figures/cloud_cost-device_consumption-cloud_consumption-distance-device=300.0.pdf}~
    \includegraphics[width=.32\linewidth]{figures/cloud_cost-device_consumption-cloud_consumption-distance-device=1000.0.pdf}
    \caption{
        Simulation results for 100 (left), 300 (center), and 1000 (right) devices;
        showing all four metrics:
        $P_{cloud}$ ($kW$) in green,
        $P_{devices}$ ($kW$) in blue,
        Distance in yellow, $\$_{cloud}$ in dark purple.
        %
        $P_{cloud}$ and $P_{devices}$ are stacked to also show the overall power consumption.
        %
        Different reconfiguration rules are indicated on the horizontal axis.
        %
        Runtime reconfiguration of the deployment opens to more opportunities to find the trade-off of cost,
        energy use, and \ac{qos} that best fits the current context.
    }
    \label{fig:results}
\end{figure*}
%
Results are summarised in \Cref{fig:results}.
%
$\Downarrow$ has the worst \ac{qos}, but also the lowest cloud cost and overall energy consumption.
%
Opposedly, $\Uparrow$ improves the \ac{qos}, but costs and energy use grow significantly.
%
The ability to reconfigure the deployment at runtime
by moving the behaviour from the cloud to the smartphones and vice versa
depending on the battery level allows to find different trade-offs between these two extremes.
